A numerical study of the solution of X-Mode equations around the hybrid resonance

### 2015-05-04 report_clean/absorption.tex
errors fixed

\subsection{Limiting Amplitude and Limiting Absorption Principle}
In this section we perform several numerical experiments to check wether the limit amplitude
principle and the limit
absorption principle are equivalent for our problem.
That is we compare the solution of the time harmonic code with the solution of the time domain staggered code.

>>>>

\subsection{Limiting Amplitude and Limiting Absorption Principle}
In this section we perform several numerical experiments to check whether the limit amplitude
principle and the limit
absorption principle are equivalent for our problem.
That is we compare the solution of the time harmonic code with the solution of the time domain staggered code.
